### 2018-09-26 Paper_HTML/Paper_HTML.Rmd
Update paper

<div class="row">
<div class="column">
<h2>Pedro Albuquerque</h2>
<p>Universidade de Brasília</p>
</div>
<div class="column">
<h2>Patrick Alves</h2>
<p>Instituto de Pesquisa Econômica Aplicada</p>
</div>
<div class="column">
<h2>Rafael Morais</h2>
<p>Universidade de Brasília</p>
</div>
<div class="column">
<h2>Cayan Portela</h2>
<p>Universidade de Brasília</p>
</div>
</div>

@@

```{r tab2}
tab2 <-  readr::read_delim(
"Job Zone & Percentual de redução
Level 1  & 31,4475%
Level 2  & 17,9420%
Level 3  & 14,4177%
Level 4  & 16,0446%
Level 5  & 7,5201%", delim = "&")

>>>>

<div class="row">
<div class="column">
<h2>Pedro Albuquerque</h2>
<p>Universidade de Brasília</p>
</div>
<div class="column">
<h2>Cayan Portela</h2>
<p>Universidade de Brasília</p>
</div>
<div class="column">
<h2>Rafael Morais</h2>
<p>Universidade de Brasília</p>
</div>
<div class="column">
<h2>Patrick Alves</h2>
<p>Instituto de Pesquisa Econômica Aplicada</p>
</div>
</div>

@@

```{r tab2}
tab2 <-  readr::read_delim(
"Job Zone & Percentual
Level 1  & 31,4475%
Level 2  & 17,9420%
Level 3  & 14,4177%
Level 4  & 16,0446%
Level 5  & 7,5201%", delim = "&")
